Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on section 2 and 3

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is the
responsibility of engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason for suchs flexibility in
the spec is to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Added to that, given the speed
the specification changes and the complexity of the language some
features are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that makes decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As previously
mentioned, all those aspects make testing \js\ engines challenging,
albeit very important given the its tremendous popularity.

@@

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. We initially selected four JS engines:
\jsc, \veight, \chakra, and \smonkey. Additionally, we also included
\hermes in the list of studied engines. The main reason for this was
to investigate how our approach would work on a recently introduced JS
engined. More about \hermes on Section~\ref{sec:hermes}.
Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used Google Chrome Lab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

>>>>

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is the
responsibility of the community to regulate the evolution of the
language. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason for such flexibility in
the spec is to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Added to that, given the speed
the specification changes and the complexity of the language some
features are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that makes decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As previously
mentioned, all those aspects make testing \js\ engines challenging,
albeit very important given the its tremendous popularity.

@@

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. We initially selected four JS engines: \jsc,
\veight, \chakra, and \smonkey. Later, we included \hermes in the list
of studied engines. The main reason was to investigate how our
approach would work on a recently introduced JS engined. More about
\hermes on Section~\ref{sec:hermes}.  Table~\ref{tab:engines} lists
the engines we analyzed. It is worth noting that we used Google Chrome
Lab's JSVU tool~\cite{jsvu} to automatically install and configure
versions of different JS engines in our host environment. This is
important as we aim to use the most recent stable versions of each
engine as to avoid reporting old and already-fixed bugs to developers.
